Analysis and figures

### 2021-04-17 analysis/03_analysis.Rmd
A bunch of edits

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(patchwork)
library(ggstance)
library(here)

>>>>

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(patchwork)
library(here)
